---
title: "DataMining1"
author: "Harika"
date: "2/27/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```
#Libraries used in this task

```{r}
library(ISLR)
library(caret)
library(dplyr)
library(glmnet)

```

#SafeBabies is the filtered dataset from Carseats with only three variables like Sales,Price,ShelveLoc
```{r}
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")
```

#To know data type of each variable 
```{r}
str(SafeBabies)
```
#Filter the data according to ShelveLoc location catagory good and bad.

```{r}

#Good ShelveLoc data
good <- filter(SafeBabies,ShelveLoc == "Good")
#Bad ShelveLoc data
bad <- filter(SafeBabies,ShelveLoc=="Bad")

```

#To maximize the profit we based on ShelveLoc following mathematical analysis is pre-required
Profit = Sales * (Price - ProductionCost)
Profit = S*(P-C)-------------(1)
S = -b1*P+b0
By doing regression we can find values of b0,b1
So equation(1) becomes 
Profit = (-b1*P+b0)*(P-C)
Profit = -b1*P^2+b1*P*C+b0*P-b0*C --------(2)
Now Profit is quadratioc equation to find value of P(Price) by doing derivative of eq(2) to 0.

#Regression for finding b0,b1 values  for good and bad ShelvLOc

```{r}
good_model <- lm(Sales ~ Price,data=good)
summary(good_model)
bad_model <- lm(Sales ~ Price,data=bad)
summary(bad_model)

```

#Finding Derivative of equation(2) by substituting b1,b0,C=55 values
```{r}
Profit_good <- expression(-0.065785*P^2 + 17.968864*P*55 + (17.968864)*P +55*0.065785) 
D1 <- D(Profit_good,'P')
P_good <- (-0.065785 *55 - 17.968864)/(2 * -0.065785)
P_good

Profit_bad <- expression(-0.055220*P^2 + 11.832984*P*55 + (11.832984)*P +55*0.055220) 
D2 <- D(Profit_bad,'P')
P_bad <- (-0.055220 *55 - 11.832984)/(2 * -0.055220)
P_bad
```
# When cost "C" is range from 40 to 85
```{r}
c <- 40:85
Price_good <- numeric(length=length(c))
for (i in seq_along(c)){
   Price_good[i] <- (-0.065785 *c[i] - 17.968864)/(2 * -0.065785)
   optimal_good <- cbind.data.frame(Varying_cost = c(40:85),Price_good)
}
Price_good

c <- 40:85
Price_bad <- numeric(length=length(c))
for (i in seq_along(c)){
   Price_bad[i] <- (-0.055220 *c[i] - 11.832984)/(2 * -0.055220)
   optimal_bad <- cbind.data.frame(Varying_cost = c(40:85),Price_bad)
}
Price_bad
```

# Plots between varying cost and respective price for good and bad shelveloc
```{r}
ggplot(optimal_good,aes(x=Varying_cost,y=Price_good))+geom_point()+ ggtitle("Varying Cost&Price-Good_ShelveLoc") +xlab("Cost") + ylab("Price") + theme(plot.title = element_text(color="blue", size=20, face="bold.italic"),
axis.title.x = element_text(color="blue", size=20, face="bold"),
axis.title.y = element_text(color="blue", size=20, face="bold")
)

ggplot(optimal_bad,aes(x=Varying_cost,y=Price_bad))+geom_point()+ ggtitle("Varying Cost&Price-Bad_ShelveLoc") +xlab("Cost") + ylab("Price") + theme(plot.title = element_text(color="brown", size=20, face="bold.italic"),
axis.title.x = element_text(color="brown", size=20, face="bold"),
axis.title.y = element_text(color="brown", size=20, face="bold")
)
```





